---
title: "Assignment B1"
output: github_document
---

The following code chunk is required to load in packages used within this assignment.

```{r}
# Load libraries required to run function
library(datateachr)
library(testthat)
library(dplyr)
library(tidyverse)
```

# Exercise 1/2 - Documenting the Creation of my New Function

## Introducing the 'Make a Difference' Function:
This function calculates the difference between 2 variables, then creates a new column to hold this data in the dataset.

```{r}
#' @description Introducing the 'Make a Difference' Function - This function calculates the difference between 2 variables, then creates a new column to hold these calculations in the dataset. 

#' INPUTS:
#' @param data The dataset containing the chosen variables to apply this function on
#' @param col1 The first chosen column/variable within the dataset.  It must contain only numeric values.
#' @param col2 The second chosen column/variable within the dataset. It must contain only numeric values.

#' OUTPUTS:
#' @return The creation of a "Difference" column in the dataset containing the calculated differences of all the data points between the 2 variables

make_a_difference <- function(data, col1, col2, ...) {
  if(!is.numeric(col1)) {
    stop("Sorry, but this function only works on numeric inputs for col1! You input a variable of class: ", class(col1))
  }
  if(!is.numeric(col2)) {
    stop("Sorry, but this function only works on numeric input for col2! You input a variable of class: ", class(col2))
  }
  return <- (mutate(data, Difference = col1-col2))
  print(return)
  }
```

# Exercise 3 - Use Examples
## Example 1
```{r}
# An example using the cancer_samples dataset, selecting only for the desired variables, and reporting the difference between perimeter_worst and perimeter_mean in malignant samples only
example1 <- cancer_sample %>% 
  select(c(diagnosis, perimeter_mean, perimeter_worst)) %>% 
  make_a_difference(cancer_sample$perimeter_worst, cancer_sample$perimeter_mean) %>% 
  filter(diagnosis == "M")
```
## Example 2
```{r}
# An example using the penguins dataset with variables containing numeric and NA values
Adelie <- palmerpenguins::penguins %>% 
  filter(species == "Adelie")
# After filtering for only the Adelie species, used the make_a_difference function to calculate the difference between bill length and depth
example2 <- Adelie %>% 
  make_a_difference(Adelie$bill_length_mm, Adelie$bill_depth_mm)
  
```

## Example 3
```{r}
# The most basic version of this function, taking the difference between tree Height and Girth values.
example3 <- make_a_difference(trees, trees$Height, trees$Girth)
```

# Exercise 4 - Testing my Function

Below I perform 4 tests to attack my function using the `testthat()`.  Here, I am checking to see if my function returns error messages when expected and produces the expected output when used correctly.

## Test 1
This test is to ensure that when a non-numeric variable is passed into the *col1* parameter, an error message is returned.

```{r}
test_that("Function returns error if non-numerical input passed into col1", {
  expect_error(make_a_difference(cancer_sample, cancer_sample$diagnosis, cancer_sample$radius_mean))
})

```

## Test 2
This test is to ensure that when a non-numeric variable is passed into *col2* parameter, an error message is returned.

```{r}
test_that("Function returns error message if non-numerical input passed into col2", {
  expect_error(make_a_difference(cancer_sample, cancer_sample$radius_mean, cancer_sample$diagnosis))
})
```

## Test 3
This test is designed to confirm a tibble is being printed following use of the function.
```{r}
test_that("Function successfully prints a tibble", {
  expect_true(is.tibble(make_a_difference(cancer_sample, cancer_sample$texture_worst, cancer_sample$texture_mean)))
})
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
