---

output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MAD - The 'Make a Difference' Package

<!-- badges: start -->
<!-- badges: end -->

The goal of the MAD package is to simplify tedious difference calculations in numeric datasets. The 'make_a_difference' function calculates the difference between two numeric variables and reports these values in a novel column labelled "Differences" within the dataset. 

## Installation

You can install the development version of MAD like so:

``` r
Use this code chunk to install the MAD package:
  devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-BriannaBris")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(MAD)
# The most basic example of this function, taking the difference between tree Height and Girth values.
tree_diff <- make_a_difference(trees, trees$Height, trees$Girth)
print(tree_diff)
```
